\documentclass[12pt,a4paper]{report}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

\usepackage[colorlinks]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}

\usepackage[numbers]{natbib}
\usepackage[nottoc]{tocbibind}

\usepackage{indentfirst}	% indent the first paragraph of a section

%
% Configure chapter/section/subsection etc printing and alignment
%
\usepackage{titlesec}

\titleformat{\chapter}[block] % shape
{\bfseries\large\centering} % format
{\thechapter.}{16pt}{\large} % label
\titlespacing{\chapter}{12pc}{0cm}{1pc}

\titleformat{\section}[block]
{\normalfont\bfseries}
{\thesection.}{14pt}{}

\newcommand{\term}{\textit}
\renewcommand{\emph}{\underline}
\newcommand{\acr}{\MakeUppercase}


\begin{document}
	\begin{titlepage}
		\begin{center}
			\thispagestyle{empty}
			\Large
			\textbf{Federated Geospatial Databases}
		\end{center}
	\end{titlepage}

	{
		\hypersetup{linkcolor=black}
		\tableofcontents
		\thispagestyle{empty}
	}
	
	\chapter{Introduction}
	\label{sec:intro}


	\todo[size={{\scriptsize}}]{Diversities in datasets! How to overcome this problem?}
	A \term{federated database} (also known as \term{integrated database} 
	\citep{Jian}) is a collection of cooperating database systems that are 
	autonomous and possibly heterogeneous \citep{Sheth}. The challenge in 
	federation arises from the heterogeneity of these autonomous databases (or 
	\term{archives} \citep{Malik}). Each  database  makes  independent choices 
	in its hardware, software, data schema, etc., and invests its resources 
	accordingly. As a result, differences arise among databases in the types of 
	network systems, operating systems, database systems, programming platforms, 
	and algorithmic techniques used. With the advance of more and more sensors 
	and automatic data acquisition tools, the number of available digital data 
	sets is ever increasing \citep{Butenuth}. This is especially true for 
	geospatial data, which are acquired by different organizations, e.g. 
	administrations like national mapping and environmental agencies, but also 
	private companies, e.g. in car navigation.
	\\

	\term{Geospatial data} is data about objects, events, or phenomena that have a location on the surface of the earth \citep{Stock}. The location may be 
	static in the short-term (e.g., the location of a road, an earthquake event, children living in poverty), or dynamic (e.g., a moving vehicle or pedestrian, even the spread of an infectious disease). Geospatial data combines location information (usually coordinates on the earth), attribute information (the characteristics of the object, event, or phenomena concerned), and often also temporal information (the time or life span at which the location and attributes exist). The terms geographical, spatial and geospatial are often used interchangeably.
	\\

	A \term{geographic information system (\acr{gis})} is a system designed to capture, store, manipulate, analyze, manage, and present all types of geographical data. The key word to this technology is Geography – this means that some portion of the data is geospatial. Interoperability of \acr{gis} is the ability to access spatial data and associated services in a distributed and heterogeneous processing environment \citep{Gong}. 
	\\


	\citep{Butenuth}: Obviously, true integration is much more than just overlaying data in a geographic information system (GIS), as it must make the relations between the individual objects in the different data sets explicit. Technically, it also means more than information fusion, if the original data sets should still be available to be used in their own right. This is a common requirement today, as different agencies are interested in maintaining control over the data they are responsible for and they have the knowledge to maintain the data properly.
	\\


	\todo[size={{\scriptsize}}]{Keep fig. 4 ?}
	\citep{Butenuth}: (Given the structural adaptation of the different data sets, the federated database can be enabled to incorporate correspondences through so called links. ) In the context of federated databases the process of identifying objects is usually restricted to one-to-one correspondences often based on simple attribute matching (like, e.g. the ISBN of books). Identifying geospatial objects, however, does not only involve simple one-to-one-relationships, as real-world objects can be represented differently in different maps. Fig. 4 shows an instance of three and two objects, respectively, e.g. a section of a water body segmented in two different ways. To represent these many-to-many correspondences, the database stores attributed one-to-one links between aggregated objects (denoted by dashed lines in Fig. 4).
	\\


	The integration of heterogeneous geospatial data offers possibilities to manually and automatically derive new information, which are not available when using only a single data source \citep{Butenuth}. Furthermore, it allows for a consistent representation and the propagation of updates from one data set to the other. However, different acquisition methods, data schemata and updating cycles of the content can lead to discrepancies in geometric and thematic accuracy and correctness which hamper the combined integration. To overcome these difficulties, appropriate methods for the integration and harmonization of data from different sources and of different types are needed.
	\\

	The major challenge in building a federation of these autonomous and heterogeneous databases is system integration \citep{Malik}.
	\\



	\chapter{Federated Geospatial Databases}
	\label{sec:fed_geodata}

	\citet{Butenuth} developed a mechanism for the semantic description of 
	geospatial objects, in order to provide the applications with a model 
	independent and uniform method to access objects with respect to thematic 
	attributes. In order to perform the integration of various types of 
	geospatial data they describe two integration algorithms. The one is for 
	matching and aligning heterogeneous vector data sets and a second one for 
	integrating raster and vector data. Both algorithms are linked to a 
	federated database as a base for any kind of complex data handling (it 
	allows for automatic object matching and for managing n:m relationships).
	\par
	Vector and raster data are the two primary types of spatial data in 
	\acr{gis} \citep{gisGeography}. The three basic symbol types for vector 
	data are points (e.g. cities in maps), lines (e.g. rivers or roads in maps) 
	and polygons (e.g. building footprints, agricultural fields). On the other 
	hand raster data is made up of pixels (also referred to as grid cells). 
	They are useful for storing data that varies continuously, e.g. elevation 
	surfaces, temperature and lead contamination. Rasters are digital aerial 
	photographs, imagery from satellites \citep{Butenuth}, digital pictures, 
	scanned maps and so on.
	\\

	\citet{Jian} introduced a method based on \acr{opengis} 
	\footnote{ \url{https://www.opengeospatial.org/}} and \acr{com} 
	\footnote{ \url{https://docs.microsoft.com/en-us/windows/win32/com/com-technical-overview}} 
	that integrates three databases, a vector database, a 
	\term{digital elevation model (\acr{dem})} database and an image database. 
	A \acr{dem} is a 3D representation of a terrain's surface – commonly of a 
	planet (e.g. Earth), moon, or asteroid – created from a terrain's elevation 
	data. \term{Open Geodata Interoperability Specification (\acr{opengis})} 
	provides a framework to create software that enables users to access and 
	process geographic data from a variety of sources across a generic computing 
	interface And \term{Component Object Model (\acr{com})} is a software 
	architecture that allows the components that made by different software 
	vendors to be combined into an integrated application. 
	\\

	\citet{Malik} presented \term{SkyQuery}, a prototype federation of 
	geographically separate astronomy databases. SkyQuery supports a federated 
	query called the \term{cross match query}. This is a spatial join query 
	that matches objects between databases, if they correspond to the same 
	astronomical body. Through these queries, the users are able to observe the 
	same sky in other wavelengths (using someone else’s data) and combine the 
	available observations into a multi-spectral data set. This immensely aids 
	in making discoveries faster and easier.
	\\

	There is not much work done on the merging of federated systems and geospatial databases.
	Interoperability among traditional geographical information systems requires solving two major problems \citep{Gong}. The former is how to access geospatial data distributed on the network. And the latter is how to allow cooperation between existing heterogeneous geospatial databases.
	\par
	The first problem is dealt with by using networking techniques based on the client/server paradigm. For example a distributed object environment, like CORBA can be used to provide interconnectivity among several geographical information systems.
	\par
	The second problem has recently been the focus of extensive researches in the field of databases. Several solutions have been identified: Schema integration based solutions aim to combine all information into a single global schema. Canonical data-model based solutions hide heterogeneity and provide a good framework for multi-model translations. Multi-database language based solutions allow users to query several information sources at the same time.
	\\ 

	\citep{Gong}: In order to solve problems, we often need the cooperation of many spatial databases, even if there are more complex spatial relationship and diversity between the existing spatial data models.
	\\



	\chapter{Federated Systems}
	\label{sec:fed_sys}
	
	To the best of our knowledge the term federated database system was 
	introduced by \citet{Hammer}. They defined federated databases as a middle 
	road that should be followed between the rigid centralization of 
	conventional database systems and the anarchy of completely diffused and 
	decentralized files.
	\\

	Federated database systems have been extensively researched \citep{Sheth, Litwin}.
	Systems consisting of multiple database systems may be characterized along three orthogonal dimensions: distribution, heterogeneity, and autonomy \citep{Sheth}. 
	\begin{itemize}
		\item \emph{Distribution}: Data may be distributed among multiple databases. These databases may be stored on a single computer system or on multiple computer systems. They can be co-located or geographically distributed but interconnected by a communication system. Data may be distributed among multiple databases in different ways. Multiple copies of some or all of the data may be maintained. These copies need not be identically structured.
		\item \emph{Heterogeneity}: The types of heterogeneities in the database systems can be divided into those due to the differences in hardware or system software and those due to the differences in the semantics of data. The differences in software refer to differences in structure, constrains or query languages. Detecting semantic heterogeneity is a much more difficult problem. It occurs when there is a disagreement about the definition, interpretation, or intended use of the same or related data (e.g. different precision of the data values). 
		\item \emph{Autonomy}: Database systems are often under separate and independent control. Those who control a autonomous database are often willing to let others share the data only if they retain control. This autonomy refers to design, communication, execution and association. 
		\begin{itemize}
			\item \emph{Design autonomy} refers to the ability of a component database system to choose its own design with respect to the data being managed, their representation, semantic interpretation, constraints etc. Consequently, heterogeneity in an federated database system is primarily caused by design autonomy among component database systems. 
			\item \emph{Communication autonomy} refers to the ability of a component database system to decide when and how it responds to a request from another component. 
			\todo[size={{\scriptsize}}]{Execution and Association}
			\item \emph{Execution autonomy} refers to its the ability execute local operations without interference from external operations, and to decide if and when to execute external operations. 
		\end{itemize}
	\end{itemize} 
	

	\todo[size={{\scriptsize}}]{??? See figure 2.}
	\citep{Jian}: A federated database can accept different heterogeneous systems and integrate them into higher level systems. They can be divided between two basic forms of interaction, cooperation and coordination. Cooperation means several systems or components use the same common datasource. While in case of coordination, the desired data will be copied among these systems or components.
	\\

	\citep{Jian}: Some times users want to access data from various distinct databases. They used to create a new database and migrate all data from other databases to the new database. This is an approach of re-enginneer databases. But the method has its obvious limitations.
	\\

	\citep{Butenuth}: Federated databases allow for integrating heterogeneous databases via a global schema, and they provide a unified database interface for global applications. Local applications remain unchanged, as they still access the databases via the local schemata.
	\\

	\citep{Malik}: An archive is naturally reluctant to forsake its autonomy – even if it is not, complete restructuring can be prohibitively expensive. Federated database architecture is designed to maintain autonomy and yet accomplish federated tasks.
	\\

	\citep{Butenuth}: Beside the general benefits of data integration, there are a lot of practical applications of integration. One is the verification and update of data sets: in order to check the currency and correctness of a data set, a second or third data set can be used to check the information. The task can be extended to provide also update capability: whenever current information is available in one data set, it can be employed to update the other sets, based on the known relations between the data sets and the known link structure between corresponding objects. Furthermore, integration can be used to provide prior information for a dedicated analysis using one data set: for example if a road network has to be updated using aerial imagery, information from existing road data can be used to partition the space and identify potential areas for new roads. Similarly, land use classifications from imagery can be used as input for a more detailed inspection of dedicated areas of interest. 
	\\




	\renewcommand{\bibname}{References}
	\bibliography{ref}
	\bibliographystyle{unsrtnat}
\end{document}
